%-------------------------
% Resume in Latex
% Author : Nitin Panwar
% Website: 
% License : MIT
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[pdftex]{hyperref}
\usepackage{fancyhdr}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.375in}
\addtolength{\evensidemargin}{-0.375in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

%-------------------------
% Custom commands
\newcommand{\resumeItem}[2]{
  \item\small{
    \textbf{#1}{: #2 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textbf{#1} & #2 \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-5pt}
}

\newcommand{\resumeSubItem}[2]{\resumeItem{#1}{#2}\vspace{-4pt}}

\renewcommand{\labelitemii}{$\circ$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=*]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  CV STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING-----------------
\begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
  \textbf{\href{http://nitin.me/}{\Large Nitin Panwar}} & Email : \href{mailto:nitinpanwar0802@gmail.com}{nitinpanwar0802@gmail.com}\\
  {Software Engineer} & Mobile : +91 9634960209 \\
\end{tabular*}

%-----------EXPERIENCE-----------------
\section{Experience}
  \resumeSubHeadingListStart
    
    \resumeSubheading
      {Bitcs}{Noida, India}
      {Software Engineer}{Feb 2022 - Present}
      \resumeItemListStart
        \resumeItem{Raven System}
          {Built out the raven system for internal tool, to submit issue, assign them, track them and add issue incidents for Ops Team workflow.}
        \resumeItem{Error Handling Framework}
          {Implemented an Error handling framework for different services we had to easily handle and show those errors on frontend.}
        \resumeItem{Improved Test Coverage}
          {Implemented Testing on both frontend and backend and improved test coverage by \textbf{+75\%} for the project.}
        \resumeItem{Tools Used}
          {React, NodeJs, GeaphQL, Sequelize, Postgres SQL, Docker, kubernetes and GCloud}
      \resumeItemListEnd

    \resumeSubheading
      {Sapio Analytics}{Mumbai, India}
      {Frontend Developer Intern - Awarded as Inter of the Month}{Aug 2021 - Nov 2021}
      \resumeItemListStart
        \resumeItem{Dashboard}
          {Built frontend Dashboard to show analytics and providing statics to users using various graphs libraries, collaborated with Backend and database team.}
        \resumeItem{Map}
          {Implememted Map on frontend for users to navigate through different state of india to see analytics and stats for that particular state. (MapBox)}
        \resumeItem{Tools Used}
          {React, MaterialUI, Mapbox, D3, Redux, plotly.js and google charts}
      \resumeItemListEnd

  \resumeSubHeadingListEnd
  



%-----------EDUCATION-----------------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Meerut Institute of Engineering and Technology}{UP, India}
      {Bachelors in Computer Science;  SGPA: 7.00}{Aug. 2019 -- Dec. 2023}
    \resumeSubheading
      {Army Public School}{Meerut, India}
      {Percentage:  74\%}{July. 2019}
  \resumeSubHeadingListEnd




%-----------PROJECTS-----------------
\section{Projects}
  \resumeSubHeadingListStart
    \resumeSubItem{Netflix Clone}
      {Watch Trailer, ratings of latest movies and add your favorite movies and TV series to your list. Created using React, Firebase, IMDB Database}
    \resumeSubItem{Hotseat API}
      {Rest API of a barber shop application - Built with Express, TypeORM and Postgres.}
    \resumeSubItem{Express Gateway}
      {Open source NodeJS framework to easily manage your Express JS routes and add subrouters.}
    \resumeSubItem{Food Ordering App}
      {Created Online Food Ordering Anroid and ios app using React Native, React navigation and Firebase.}
  \resumeSubHeadingListEnd

%
%--------PROGRAMMING SKILLS------------
\section{Programming Skills}
 \resumeSubHeadingListStart
   \item{
     \textbf{Languages}{: Javascript, Typescript, Go, Python, SQL, GraphQL}
    }
    \item{
     \textbf{Technologies}{: React, Google Cloud, Docker, Kubernetes and Git}
    }

 \resumeSubHeadingListEnd
 
%  ------------------ Courses ---------------
\section{Courses}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Docker Mastery: with Kubernetes +Swarm from a Docker Captain
}{20 hrs}
      {Udemy}{Jan - March 2022}
    \resumeSubheading
      {SQL and PostgreSQL: The Complete Developer's Guide
}{22 hrs}
      {Udemy}{Sept - Nov 2021}
    \resumeSubheading
      {Microservices with NodeJS and React}{54 hrs}
      {Udemy}{Jan - June 2021}
  \resumeSubHeadingListEnd
%-------------------------------------------
\end{document}
